Ground state energy of quantum dots using the coupled cluster method

### 2018-04-27 project_2/article/article.tex

>>>>

    \subsection{Constructing the matrix elements}
        Having found the equations needed in order to find an estimate to the
        ground state energy using the coupled cluster doubles approximation is a
        well and dandy. But, we need basis functions to create the matrix
        elements needed to feed into the coupled cluster code.  Often these
        basis functions are not known and we have to use an approximation or
        utilize Hartree-Fock to create more optimized basis functions.

        \subsubsection{Harmonic oscillator basis}
            We will be looking at a system of two-dimensional quantum dots with
            a Coulomb repulsion.  If we assume, or make it so, that the
            repulsive two-body part is small we can use the harmonic oscillator
            functions as our basis functions and compute the matrix elements
            before feeding it into the coupled cluster code. We will label these
            basis functions using greek letters, viz.
            \begin{align}
                h\ket{\alpha} = \epsilon_{\alpha}\ket{\alpha}.
            \end{align}
            In polar coordinates we can write the harmonic oscillator
            wavefunction for a single particle in two dimensions\footnote{Note
            that this is without spin. As we are looking at fermions this means
            that each mode of the harmonic oscillator functions will be repeated
            twice.}.
            \begin{align}
                \phi_{nm}(r, \theta)
                &=
                N_{nm}
                %a\sqrt{\frac{n!}{\pi(n + \abs{m})!}}
                (ar)^{\abs{m}}L_n^{\abs{m}}(a^2 r^2)e^{-a^2 r^2/2}
                e^{im\theta},
            \end{align}
            where $a = \sqrt{m\omega/\hbar}$ is the Bohr radius, $L_n^{\abs{m}}$
            is the associated Laguerre polynomials, $n$ and $m$ are the
            principal and azimuthal quantum numbers respectively and $N_{nm}$ is
            a normalization constant given by
            \begin{align}
                N_{nm}
                &= a\sqrt{\frac{n!}{\pi(n + \abs{m})!}}.
            \end{align}

            From E. Anisimovas and A. Matulis\cite{anisimovas1998energy} we can
            get an analytical expression for the two-body matrix elements.
